Minimizing post-shock forecasting error through aggregation of outside information

### 2020-12-31 Revision/manuscript.tex
revised Section 5.2

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials. The estimated shock-effects for $\alpha_i$ are $-0.922, -7.063, -5.777, -6.395, -4.207$ for $i = 2, \ldots, 6$, respectively. Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$. Note that non-uniqueness problems will not occur in this analysis since the conditions of Proposition \ref{uniqueness} are satisfied. To avoid the effect of  unit differences on weighting, we center and scaled the covariates in weights computation but not in the model of $y_{i,t}$. For $\hat{\alpha}_{\rm wadj}$, we observe that 
$
  \mathbf{W}^*= (0.000,0.000, 0.000, 0.273, 0.727)
$
and 
$
  \Vert\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\Vert_2 = 3.440.
$
Note that the norm is computed using the $k$-dimensional Euclidean metric. The solution $\mathbf{W}^*$ suggests that the shock effect of interest is very similar to the September 25, 2008 shock effect and  the November 27, 2014 shock effect.

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products, such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Mac sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Mac account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. near the release of MacBook series on November, 10th, 2020. In particular, in recent years, we observe that it usually takes two or more than two days for the shock to take effect on the stock price in the case of Apple Inc. Therefore, different from Section \ref{forecasting}, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.} Similar to Section \ref{forecasting}, we use an AR(1) model to forecast the stock price of Apple Inc. We consider 20 trading days data for the time series of interest and time series in the donor pool. Likewise, all the estimates will be adjusted for inflation. Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$ in replace of the one in Section \ref{modelsetup}. As a result, a generalized weighting of Section \ref{constructionofestimators} is used. To be specific, we mean 
  \begin{align*}
    \mathbf{X}_1 = \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \quad \text{ and } \quad 
    \mathbf{X}= \begin{pmatrix}
      \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
    \end{pmatrix},
  \end{align*}
  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ stands for the covariates from time $t = T_i^* +1$ to $t = T_i^*+2$. The model $\mc{M}_2$ is then generalized to 
  \begin{align*}
    \mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
\end{array}
  \end{align*}
  where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
  \item \textbf{Selection of covariates.} Different to Section \ref{forecasting}, we consider only  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select AR(3) for S\&P 500 index prices and AR(1)  for 13 Week treasury bill rates. We used Ljung-Box tests to test for model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. Then, we use 2-ahead forecasts to predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date as  in the middle of 20 trading days for 2017, 2018, and 2019.  The shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively. Those dates are the past dates when Apple introduced new series of MacBook products in the corresponding year.
\end{enumerate}

The covariates and response of time series in the donor pool are adjusted for inflation. The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively. Using  the same treatment of the covariates in computing $\mathbf{W}^*$ as in Section \ref{forecasting}, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.673.
$ It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.

@@

As we can see from Figure \ref{Fig3}, the post-shock forecasts perform nearly perfectly. The unadjusted forecast misses the post-shock by 0.919 dollars. The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.047, 0.035, and 0.031 dollars. In other words, the true shock effect is nearly fully recovered by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$. It implies that the construction of donor pool is successful. To explain, it appears as a trend that in recent 3 years, Apple inc. only updates the hardware of the MacBook series in the release of every year without much redesign, and improves the their hardware performance significantly \citep{apple2017, apple2018, apple2019} . It is the case for the release in 2020 as well. The new MacBook series consider M1 chip invented by Apple inc. itself in replace of chips by Intel inc. in the past years, and their CPU speed improves significantly; the M1 chip enables  Mac users to use the apps developed in iPhone and thus run a greater range of applications than before \citep{apple2020}. Therefore, in this example, our analysis is similar to \cite{baumeister2014real} in that the  forecast is conditioned on past shocks and the shock is within the range of historical experience.

>>>>

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials. The estimated shock-effects for $\alpha_i$ are $-0.922, -7.063, -5.777, -6.395, -4.207$ for $i = 2, \ldots, 6$, respectively. Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$. Note that non-uniqueness problems will not occur in this analysis since the conditions of Proposition \ref{uniqueness} are satisfied. To avoid the effect of  unit differences on weighting, we centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$. For $\hat{\alpha}_{\rm wadj}$, we observe that 
$
  \mathbf{W}^*= (0.000,0.000, 0.000, 0.273, 0.727)
$
and 
$
  \Vert\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\Vert_2 = 3.440.
$
Note that the norm is computed using the $k$-dimensional Euclidean metric. The solution $\mathbf{W}^*$ suggests that the shock effect of interest is very similar to the September 25, 2008 shock effect and  the November 27, 2014 shock effect.

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Mac sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Mac account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. near the release of MacBook series on November, 10th, 2020. In particular, in recent years, we observe that it usually takes two or more than two days for the shock to take effect on the stock price in the case of Apple Inc. Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc. We consider 20 trading days data for the time series of interest and time series in the donor pool. All the estimates will be adjusted for inflation. Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$ in replace of the one in Section \ref{modelsetup}. As a result, a generalized weighting of Section \ref{constructionofestimators} is used. To be specific, we mean 
  \begin{align*}
    \mathbf{X}_1 = \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \quad \text{ and } \quad 
    \mathbf{X}= \begin{pmatrix}
      \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
    \end{pmatrix},
  \end{align*}
  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ stands for the covariates from time $t = T_i^* +1$ to $t = T_i^*+2$. The model $\mc{M}_2$ is then generalized to 
  \begin{align*}
    \mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
\end{array}
  \end{align*}
  where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
  \item \textbf{Selection of covariates.} \textcolor{red}{We consider   S\&P 500 index prices and 13 Week treasury bill rates as covariates.} In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select AR(3) for S\&P 500 index prices and AR(1)  for 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. Then, we use 2-ahead forecasts to predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date as  in the middle of 20 trading days for 2017, 2018, and 2019.  The shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively. Those dates are the past dates when Apple Inc. introduced new series of MacBook computers in the corresponding year.
\end{enumerate}

The covariates and response of time series in the donor pool are adjusted for inflation. The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively. \textcolor{red}{We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.} As a result, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.673.
$ It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.

@@

As we can see from Figure \ref{Fig3}, the post-shock forecasts perform nearly perfectly. The unadjusted forecast misses the post-shock by 0.919 dollars. The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.047, 0.035, and 0.031 dollars, respectively. In other words, the true shock effect is nearly fully recovered by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$. It implies that the construction of donor pool is successful. To explain, it appears as a trend that in recent 3 years, Apple inc. only updates the hardware of the MacBook series in the release of every year without much redesign, and improves the their hardware performance significantly \citep{apple2017, apple2018, apple2019} . It is the case for the release in 2020 as well. The new MacBook series consider M1 chip invented by Apple inc. itself in replace of chips by Intel inc. in the past years, and their CPU speed improves significantly; the M1 chip enables  Mac users to use the apps developed in iPhone and thus run a greater range of applications than before \citep{apple2020}. Therefore, in this example, our analysis is similar to \cite{baumeister2014real} in that the  forecast is conditioned on past shocks and the shock is within the range of historical experience. \textcolor{red}{In other words, the shock in this example is not unprecedented.}
